### 2019-12-05 upper.tex
Ring communication pattern

>>>>

      \section{$O(k)$-competitive algorithm for the ring}

      \maciek{todo}

      We know that the lower bound is $k$ for the ring communication pattern (cite Marcin-Chen).
      The simple matching (assymptotically \maciek{maybe it is easy to have $k$ exactly?}) upper bound is to fix the reconfiguration to be the cyclic shift. We reconfigure upon encountering inter-cluster request. We use phases: upon discovering the edge on each cut we charge OPT 1 and reset counters.
